Proportions of extreme values the usual direction

### 2021-04-17 analysis/howto.Rmd
stop using gh actions, rerender main figs

To run a subset locally, you can run `mcdb_pipeline_demo.R`. This will run the pipeline on the first 100 communities in the Mammal Community Database. It takes [time] on a MacBook Air with 8GB memory and creates a [size] cache file.

>>>>

To run a subset locally, you can run `mcdb_pipeline_demo.R`. This will run the pipeline on the first 50 communities in the Mammal Community Database, drawing up to 200 samples from each feasible set. It takes about 20 minutes on a MacBook Air with 8GB memory and creates a 51 MB cache file.

### 2021-04-17 analysis/reports/submission2/table1_extreme_values.Rmd
stop using gh actions, rerender main figs

---
title: "Proportions of extreme values the usual direction"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
    word_document:
        df_print: kable
        toc: false
---

>>>>

---
title: "Proportions of extreme values the usual direction"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true
    # word_document:
    #     df_print: kable
    #     toc: false
---
